Har en persons høyde innvirkning på lønnen?

### 2020-10-11 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
Formatering

---
title: "Har en persons høyde innvirkning på lønnen?"
author:
- Katrine Hope
- Karl-Gunnar Severinsen
subtitle: Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20
output:
  html_notebook: default
  pdf_document: default
fontsize: 12pt
linestretch: 1.5
classoption: twoside
---

```{r setup, echo = FALSE}
library(modelr)
library(ggplot2)
library(knitr)
library(tinytex)
library(tidyverse)
library(ggpubr)
library(dplyr)
options(scipen = 999)
```

## Introduksjon

@@

```{r height_income, echo=FALSE}
m1 <- ggplot(heights, 
             mapping = aes(x = height_cm, 
                           y = inntekt, 
                           col = inntekt)) +
  geom_point()
m2 <- ggplot(heights_liminc, 
             mapping = aes(x = height_cm, 
                           y = inntekt, 
                           col = inntekt)) +
  geom_point()

@@

```{r boxplot, echo=FALSE}
m3 <- ggplot(heights,
                mapping = aes(
                  x = height_cmInt,
                  y = inntekt)) +
        geom_boxplot(colour= "darkred",
                     fill = "cornflowerblue") +
  theme(panel.background = element_rect(fill = "pink"))
m4 <- ggplot(heights_liminc, 
               mapping = aes(
                 x = height_cmInt, 
                 y = inntekt)) +
        geom_boxplot(colour = "darkred",
                     fill = "darkolivegreen") +
  theme(panel.background = element_rect(fill = "pink"))

@@

```{r educ_facet, echo=F}
m7 <- ggplot(data = heights, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(education, 
                           n =2)) +
  geom_point(aes(colour = cut_number(education, 
                                     n = 2)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

m8 <- ggplot(data = heights_liminc, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(education, 
                           n =2)) +
  geom_point(aes(colour = cut_number(education, 
                                     n = 2)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

@@

```{r age_facet, echo=F}
m9 <- ggplot(data = heights, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(age, 
                           n =3)) +
  geom_point(aes(colour = cut_number(age, 
                                     n = 3)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

m10 <- ggplot(data = heights_liminc, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(age, 
                           n =3)) +
  geom_point(aes(colour = cut_number(age, 
                                     n = 3)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

ggarrange(m9, m10)

>>>>

---
title: "Har en persons høyde innvirkning på lønnen?"
author:
- Katrine Hope
- Karl-Gunnar Severinsen
subtitle: Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20
output:
  pdf_document: default
  html_notebook: default
fontsize: 12pt
linestretch: 1.5
classoption: twoside
---

```{r setup, message=FALSE, echo = FALSE}
library(modelr)
library(ggplot2)
library(knitr)
library(tinytex)
library(tidyverse)
library(ggpubr)
library(dplyr)
options(scipen = 999)
```

\newpage
## Introduksjon

@@

```{r height_income, echo=FALSE}
m1 <- ggplot(heights, 
             mapping = aes(x = height_cm, 
                           y = inntekt, 
                           col = inntekt)) +
  geom_point()

m2 <- ggplot(heights_liminc, 
             mapping = aes(x = height_cm, 
                           y = inntekt, 
                           col = inntekt)) +
  geom_point()

@@

```{r boxplot, echo=FALSE}
m3 <- ggplot(heights,
                mapping = aes(
                  x = height_cmInt,
                  y = inntekt)) +
        geom_boxplot(colour= "darkred",
                     fill = "cornflowerblue") +
  theme(panel.background = element_rect(fill = "pink"))

m4 <- ggplot(heights_liminc, 
               mapping = aes(
                 x = height_cmInt, 
                 y = inntekt)) +
        geom_boxplot(colour = "darkred",
                     fill = "darkolivegreen") +
  theme(panel.background = element_rect(fill = "pink"))

@@

```{r educ_facet, echo=F}
m7 <- ggplot(data = heights, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(education, 
                           n = 2)) +
  geom_point(aes(colour = cut_number(education, 
                                     n = 2)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

m8 <- ggplot(data = heights_liminc, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(education, 
                           n = 2)) +
  geom_point(aes(colour = cut_number(education, 
                                     n = 2)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

@@

```{r age_facet, echo=F}
m9 <- ggplot(data = heights, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(age, 
                           n = 3)) +
  geom_point(aes(colour = cut_number(age, 
                                     n = 3)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

m10 <- ggplot(data = heights_liminc, 
             mapping = aes(x = height_cm, 
                           y = inntekt)) +
    facet_wrap(~cut_number(age, 
                           n = 3)) +
  geom_point(aes(colour = cut_number(age, 
                                     n = 3)), 
             show.legend = F) +
  geom_smooth(method = "lm", 
              se = FALSE)

ggarrange(m9, m10)
```
